This is where you acknowledge contributors that are not authors. Someone may have provided you thoughts and data samples and didn't feel they had contributed enough. Any individuals you name must be contacted to check that they don't think they should be authors, and to approve you naming them. This is not true of organizations, such as funding bodies. However, they will have specific language to include. Check with them. Make sure you identify any funding sources. This is important for public access mandates and intellectual property, as well as for reporting to the sponsors. Note that identifying sponsors here will create a permanent link, that will carry with it some specific responsibilities and funding flows for IP. So don't just throw in everyone who funds you. Be appropriate. Here's an example in italics (but don't italicize):

{\it
The authors wish to acknowledge the support of the National Science Foundation Award 1636933, National Institutes of Health (Grant R01HL136205). Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation or the National Institutes of Health.

CL was funded by the International Post-doctoral Exchange Programme of the National Postdoctoral Management Committee of China and Emory University. We also would like to thank Arvind Ananthan and MathWorks, for their valuable assistance, free licenses to competitors and financial support of the Challenge.  Finally, we thank all the Challenge competitors themselves, without whom there would be no competition. } 

You must acquire the approval of anyone you acknowledge. You can't just thank people for advice or helping without asking them, because it may imply they approve of your work.
In this example, only the named person needs to be contacted for approval because they represent the company that is mentioned (MathWorks). If naming a company, it is important to check with a representative of the company to avoid any friction. They may not want to be associated with your article.
